\input{preamble}

\newcommand{\trnas}{Translation}
\newcommand{\dic}{Dictionary}
\newcommand{\review}{Review}

\begin{document}

\input{titlepage}
\tableofcontents
\clearpage
\section{Quantum cryptography with coherent states}
\input{qcwcs}

\section{Quantum cryptography: public key distribution and coin tossing}
\input{qc-pkd-and-ct}


\section{Towards practical and fast Quantum Cryptography}
\input{tp-and-fqc}


\section{Quantum cryptography based on Bell's theorem}
\input{qcb-on-bt}

\section{High error-rate quantum key distribution for long-distance communication }

\input{kmb09}

\section{Decoy state quantum key distribution}

\input{dsqkd}


\section{Quantum Key Distribution Protocols: A Review}

\input{qkdp-a-r}

\section{Quantum key distribution protocol with private-public key}
\input{qkd-w-ppk}

\section{Quantum cryptography protocols robust against photon number splitting attacks for weak laser pulse implementations}
\input{sarg04}

\section{Quantum key distribution based on random grouping bell state measurement}
\input{qkd-b-rgbsm}


\section{Quantum-key-distribution (qkd) networks enabled by software-defined networks (sdn}
ss

\section{Quantum key distribution: a networking perspective}
\input{qkd-network}

\clearpage
\section{Scientific report}
%Я Галов Кирилл Алексеевич. Я учусь в аспирантуре Донского Технического Университета на кафедре "Кибербезопасность информационных систем". Основным направлением моей научной деятельности является квантовая криптография.

%Квантовая криптография - это раздел криптографии, который занимается изучением способов защиты информации при помощи квантовых технологий и свойств квантовых объектов. Это важное направление науки, потому что современная классическая криптография основывается на предположении об ограниченности вычислительной мощности злоумышленника и на том, что не существует эффективного алгоритма для взлома шифров. Квантовая криптография основывается на нерушимых законах физики, что делает ее более надежной, чем классическую.

%Я только начал свой путь молодого ученого и еще не успел опубликовать значимого количества научных работ. Однако, за первые пол года учебы в аспирантуре я успел поучаствовать в конференции, материалы которой попадут в РИНЦ и стать соавтором работы по теме безопасности в сети интернет, которая в скором времени должна быть опубликована в Scopus.

%Мне нравится заниматься наукой, это очень интересно и полезно для общества. Надеюсь через несколько лет опубликовать достаточное количество научных статей и защитить диссертацию по теме квантового распределения ключей.

I am Kirill Alekseyevich Galov. I am a postgraduate student at Don State Technical University, department of Cyber Security of Information Systems. The main direction of my scientific activity is quantum cryptography.

Quantum cryptography - is a section of cryptography, which is engaged in the study information protection methods with the quantum technologies and properties of quantum objects. It is an important branch of science because modern classical cryptography is based on the assumption that the computing power of the attacker is limited and that there is no effective algorithm for breaking ciphers. Quantum cryptography is based on the unbreakable laws of physics, which makes it more secure than classical cryptography.

I have just begun my journey as a young scientist and have not yet had time to publish a significant number of scientific papers. However, in the first half year of my postgraduate studies I had time to participate in a conference, the materials of which will be published in the Russian Science Citation Index, and become co-author of papers on Internet security, which are due for publication in Scopus in the near future.

I like doing science, it is very interesting and useful for society. I hope in a few years to publish a sufficient number of scientific articles and defend my dissertation on quantum key distribution.


\clearpage

\pagenumbering{gobble}
\section*{Отзыв научного руководителя на используемую литературу}
Я, Черкесова Лариса Владимировна, научный руководитель аспиранта первого года обучения Галова Кирилла Алексеевича даю согласие на использование аспирантом следующей литературы:
\begin{enumerate}
	\item Huttner B. et al. Quantum cryptography with coherent states //Physical Review A. – 1995. – Т. 51. – №. 3. – С. 1863.
	\item Bennett C. H., Brassard G. Quantum cryptography: Public key distribution and coin tossing //arXiv preprint arXiv:2003.06557. – 2020.
	\item Gisin N. et al. Towards practical and fast quantum cryptography //arXiv preprint quant-ph/0411022. – 2004.
	\item Ekert A. K. Quantum cryptography based on Bell’s theorem //Physical review letters. – 1991. – Т. 67. – №. 6. – С. 661.
	\item Khan M. M., Murphy M., Beige A. High error-rate quantum key distribution for long-distance communication //New Journal of Physics. – 2009. – Т. 11. – №. 6. – С. 063043.
	\item Lo H. K., Ma X., Chen K. Decoy state quantum key distribution //Physical review letters. – 2005. – Т. 94. – №. 23. – С. 230504.
	\item Singh H., Gupta D. L., Singh A. K. Quantum key distribution protocols: a review //Journal of Computer Engineering. – 2014. – Т. 16. – №. 2. – С. 1-9.
	\item Serna E. H. Quantum key distribution protocol with private-public key //arXiv preprint arXiv:0908.2146. – 2009.
	\item Scarani V. et al. Quantum cryptography protocols robust against photon number splitting attacks for weak laser pulse implementations //Physical review letters. – 2004. – Т. 92. – №. 5. – С. 057901.
	\item Song D., Chen D. Quantum Key Distribution Based on Random Grouping Bell State Measurement //IEEE Communications Letters. – 2020. – Т. 24. – №. 7. – С. 1496-1499.
	\item Wang H., Zhao Y., Nag A. Quantum-key-distribution (qkd) networks enabled by software-defined networks (sdn) //Applied Sciences. – 2019. – Т. 9. – №. 10. – С. 2081.
	\item Mehic M. et al. Quantum key distribution: a networking perspective //ACM Computing Surveys (CSUR). – 2020. – Т. 53. – №. 5. – С. 1-41.
\end{enumerate}
Содержание данной литературы соответствует специальности 09.06.01 «Информатика и вычислительная техника». Информация является актуальной и полезной для самостоятельного изучения.\\
\bigskip

%\begin{centering}
\rightline{проф. каф. «КБИС», д.ф.-м.н. \hspace{0.5cm} \underline{\hspace{3cm}} \hspace{0.5cm} Черкесова Л. В}

%\end{centering}


\end{document}